---
title: "Tidymodels template"
author: "<Your name here>"
---


# Setup

```{r}
library(tidymodels)
library(tidyverse)
library(tictoc)  # measure computation time
library(<other_package_you_might_need_for_modelling>)  # tidymodels uses existing packages for modelling so you need to make them available

```



# Data

Import data:

```{r}
d_path <- "Enter data path here"
d <- read_csv(d_path)
```


Split into train and test:

```{r}
set.seed(42)
d_split <- initial_split(d)
d_train <- training(d_split)
d_test <- testing(d_split)
```



# Define model

See [here](https://www.tidymodels.org/find/parsnip/) an overview of machine learning models supported by `{parsnip}`.

```{r}
mod1 <-
  <enter_parsnip_model_name_here>(
    mode = "<choose_regression_or_classification>",
           cost_complexity = tune())
```



# Define Cross validation scheme

```{r}
set.seed(42)
rsmpl <- vfold_cv(d_train)
```



# Define preprocessing (recipe)

```{r}
rec1 <- recipe(<enter_output_variable> ~  ., data = d_train)
```



# Define workflow

```{r}
wf1 <-
  workflow() %>% 
  add_model(mod1) %>% 
  add_recipe(rec1)
```



# Tune and fit the workflow

```{r}
tic()
wf1_fit <-
  wf1 %>% 
  tune_grid(
    resamples = rsmpl)
toc()
```


# Finalize workflow with best tuning parameter values

best candidate:

```{r}
show_best(wf1_fit)
```




finalize wf:

```{r}
wf1_final <-
  wf1 %>% 
  finalize_workflow(select_best(wf1_fit))
```


Fit with best parameter values:

```{r}
wf1_fit_final <-
  wf1_final %>% 
  last_fit(d_split)
```



# Performance in test set

```{r}
# Modellgüte im Test-Set:
collect_metrics(wf1_fit_final)
```



